---
title: "Covid91 vaccine study Final2024"
author: "Isabela Bercian!"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`May 2025`" 
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(forcats)
FinalDat <-read.csv(file="finalSumr2024.csv",header=TRUE)
#recode to remove the annoying "X" from the dataframe
FinalData <- FinalDat  %>% select(-one_of("X"))
FinalData <- FinalData %>%
mutate(across(where(is.character), as.factor))
```

# Introduction

A new  preventative vaccine (covid921) is under test in clinical trials. Given the nature of this vaccine it is suspected that the drug may exhibit different effectiveness across the variety of subpopulations tracked. Consider population subgroups by gender( guys and gals), drug use, and sexual orientation. Write a complete report that separately considers this drug for each subgroup and your recommendations as to whether people in the subgroup should take the vaccine. Structure your report in four sections each devoted to one of the four subgroups, use null and alternative hypothesis statements and correct statistical verbage when referencing p-values in conclusions.

## Males

Is the Covid vaccine effetive in males?

$H_0$: The new preventative vaccine (Covid921) does not exhibit any effectivness on males.  
$H_A$: The new preventative vaccine (Covid921) does exhibit effectivness on male.

cat-cat

```{r}
Males = FinalData[FinalData$sex=='M',]
head(Males)
```

## Graphical Results

```{r}
barchartGC(~infected + treatment,data=Males)
barchartGC(~infected + treatment,data=Males, type="percent")
```

This graph demonstrates that the vaccine is effective in preventing COVID-19 in males, as fewer men who received the vaccine contracted the virus compared to those who received the placebo.


## Females


## LGBTQ



## Druggies


# Overall Results and Conclusions